DraftOne

### 2016-07-12 writing/JSSDraft/JSSDraft.Rmd
Updating bib file to include Strickland

\citet{Strickland2013} used a simulation study to investigate the effects of measurement error resulting from instrument imprecision and spacial misalignment on the estimates of health effects related to ambient air pollutant concentrations.  They first used air-quality measurements obtained from several networks of monitoring stations in Atlanta to estimate various distributional properties associated with pollutant concentrations, including spatial and temporal autocorrelation. They used these estimates to generate daily two-dimensional pollutant fields for Atlanta at 5 km grids, producing "true" population-weighted average pollutant concentrations (TPWA).  They then simulated grid-specific counts of daily ED visits using TPWA as a covariate, among others.

>>>>

\citet{Strickland2015} used a simulation study to investigate the effects of measurement error resulting from instrument imprecision and spacial misalignment on the estimates of health effects related to ambient air pollutant concentrations.  They first used air-quality measurements obtained from several networks of monitoring stations in Atlanta to estimate various distributional properties associated with pollutant concentrations, including spatial and temporal autocorrelation. They used these estimates to generate daily two-dimensional pollutant fields for Atlanta at 5 km grids, producing "true" population-weighted average pollutant concentrations (TPWA).  They then simulated grid-specific counts of daily ED visits using TPWA as a covariate, among others.
